Classless Java

### 2015-11-16 paper/sections/RelatedWork.tex
Discussion on MetaFjig

- MetaFJig*~\cite{}
\yanlin{Maybe Marco can help with the text for MetaFJig?}

>>>>

Here (compile/load time) code generation come at the rescue: 
if for a certain feature (\mixin in our case) it is possible to use the original language syntax to
\emph{express-describe} any specific instantiation of such feature
(annotating a class and provide getters), then we can insert in the compilation process a tool that exam and enrich the code before compilation. No need to modify the original, source, we can work on temporary enriched source.
Java is a particular good candidate for this kind of manipulation since it already provide ways to define and integrate such tools in its own compilation process.

Other languages offers even stronger support to safe code manipulation:
Template Haskell~\cite{}, F\# (type providers)~\cite{} and MetaFjig (Active Libraries)~\cite{}
all allows to execute code at compile time and to generate code/classes that are transparently integrated in the program that is being generated/processed/compiled.
In particular, MetaFjig offers a property called \emph{meta-level-soundness}. In short this property ensures by construction that library code (even if wrong or non nonsensical) would never generate ill-typed code. This is roughly equivalent to what we state and manually proof in Lemma 2 for our particular transformation.
Since MetaFjig is not working on annotated classes, there is no direct equivalence on the overall theorem of safety we shown.
